Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
edits to 2.2

To make this concrete we need to define what programs actually are and
what form $\probability[p |\mathcal{D},\theta]$ takes.
We represent programs as $\lambda$-calculus expressions.
$\lambda$-calculus is a formalism for expressing functional programs
that closely resembles the Lisp programming language.
$\lambda$-calculus includes variables, function application, and the ability to create new functions.
Throughout this paper we will write $\lambda$-calculus expressions in Lisp syntax.
Our programs are all strongly typed.
We use the Hindley-Milner polymorphic typing system~\cite{pierce} which is used in functional languages like OCaml.
Variables that range over types are always written using lowercase Greek letters
and we write $\alpha\to \beta$ to mean a function that takes as input type $\alpha$
and returns something of type $\beta$.
We use the notation $p:\tau$ to mean that the $\lambda$-calculus expression $p$
has the type $\tau$.
For example, to describe the type of the identity function
we would say \code{(lambda (x) x)}$:\alpha\to \alpha$.
We say a type $\alpha$ \emph{unifies} with $\tau$ if every expression
$p:\alpha$ also satisfies $p:\tau$. Furthermore, the act of \emph{unifying}
a type $\alpha$ with $\tau$ is to introduce constraints on the type
variables of $\alpha$ to ensure that $\alpha$ unifies with $\tau$.
See Supplement for more detail on program representation.
With this notation in hand we now define DSLs:

@@

Why enumerate, when the program synthesis community has invented many
sophisticated algorithms that search for programs?~\cite{solar2008program,schkufza2013stochastic,feser2015synthesizing,osera2015type,polozov2015flashmeta}.
We have two reasons:
(1) A key point of our work is that learning the DSL, along with a neural recognition model, can make program induction tractable, even if the search algorithm is very simple.
(2) Enumeration is a general approach that can be applied to any program induction problem. Many of these more sophisticated approaches require special conditions on
  the space of of programs.

A main drawback of an enumerative search algorithm is that we have no
efficient means of solving for arbitrary constants that might occur in the
program. In Sec.~\ref{regressionSection},
we will show how to find programs with real-valued constants
by automatically differentiating through the program and setting the constants using gradient descent.
%% In Sec.~\ref{textSection}
%% we will show that the bottom-up neural recognition model can learn
%% which discrete constants should be included in a program.

>>>>

To make this concrete we need to define what programs actually are and
what form $\probability[p |\mathcal{D},\theta]$ takes.
We represent programs as $\lambda$-calculus expressions.
$\lambda$-calculus is a formalism for expressing functional programs
that closely resembles the Lisp programming language.
$\lambda$-calculus includes variables, function application, and the ability to create new functions.
Throughout this paper we will write $\lambda$-calculus expressions in Lisp syntax.
Our programs are all strongly typed.
We use the Hindley-Milner polymorphic typing system~\cite{pierce} which is
used in functional programming languages like OCaml.
Type variables are always written using lowercase Greek letters
and we write $\alpha\to \beta$ to mean a function that takes an input of type $\alpha$
and returns something of type $\beta$.
We use the notation $p:\tau$ to mean that the $\lambda$-calculus expression $p$
has the type $\tau$.
For example, to describe the type of the identity function
we would say \code{(lambda (x) x)}$:\alpha\to \alpha$.
We say a type $\alpha$ \emph{unifies} with $\tau$ if every expression
$p:\alpha$ also satisfies $p:\tau$. Furthermore, the act of \emph{unifying}
a type $\alpha$ with $\tau$ is to introduce constraints on the type
variables of $\alpha$ to ensure that $\alpha$ unifies with $\tau$.
See Supplement for more detail on program representation.
With this notation in hand we now define DSLs:

@@

Why enumerate, when the program synthesis community has invented many
sophisticated algorithms that search for programs?~\cite{solar2008program,schkufza2013stochastic,feser2015synthesizing,osera2015type,polozov2015flashmeta}.
We have two reasons:
(1) A key point of our work is that learning the DSL, along with a neural recognition model, can make program induction tractable, even if the search algorithm is very simple.
(2) Enumeration is a general approach that can be applied to any program induction problem. Many of these more sophisticated approaches require special conditions on
  the space of programs.

A drawback of using an enumerative search algorithm is that we have no
efficient means of solving for arbitrary constants that might occur in the
program. In Sec.~\ref{regressionSection},
we will show how to find programs with real-valued constants
by automatically differentiating through the program and setting the constants using gradient descent.
%% In Sec.~\ref{textSection}
%% we will show that the bottom-up neural recognition model can learn
%% which discrete constants should be included in a program.
